Installation instructions are provided for Linux (Ubuntu/Debian) and Windows. All paths are relative to the corresponding root of unpacked archive files. The Structure from Motion tools are available online, or provided as Windows/Linux binaries in sfm/. Libraries are also available online, or provided in the mentioned versions as source code in lib/.

\begin{enumerate}
\item Install OpenCV (I used 2.4.1) - http://opencv.willowgarage.com

    Linux Ubuntu, older version (2.3):
    \begin{verbatim}
$ sudo add-apt-repository ppa:gijzelaar/cuda
$ sudo add-apt-repository ppa:gijzelaar/opencv2.3
$ sudo apt-get update
$ sudo apt-get install libcv-dev
    \end{verbatim}

    Linux Ubuntu, newest version from source:
    \begin{verbatim}
$ sudo apt-get install cmake pkg-config libavformat-dev libswscale-dev \
  libavcodec-dev libavfilter-dev libpython2.7 python-dev python2.7-dev \
  python-numpy libgstreamer0.10-0-dbg libgstreamer0.10-0 \
  libgstreamer0.10-dev libgstreamer-plugins-base0.10-dev libdc1394-22-dev \
  libdc1394-22 libdc1394-utils libavformat-dev libxine-dev \
  libgstreamer0.10-dev libgstreamer-plugins-base0.10-dev libv4l-dev \
  libtbb-dev libqt4-dev libgtk2.0-dev openni-dev sphinx-common
$ mkdir release && cd release
$ cmake -D CMAKE_BUILD_TYPE=RELEASE -D CMAKE_INSTALL_PREFIX=/usr/local -D \
  BUILD_PYTHON_SUPPORT=ON -D WITH_QT=ON -D WITH_XINE=ON -D WITH_V4L=ON -D \
  WITH_OPENGL=ON -D WITH_OPENNI=ON -D WITH_TBB=ON -D BUILD_DOCUMENTATION=ON \
  -D BUILD_EXAMPLES=ON release ..
$ make && sudo make install
    \end{verbatim}

    Windows: \\
     Run binary executable from http://sourceforge.net/projects/opencvlibrary/files/opencv-win/2.4.0/


\item Install Point Cloud Library (I used 1.6) - http://pointclouds.org

    Linux Ubuntu:
    \begin{verbatim}
$ sudo add-apt-repository ppa:v-launchpad-jochen-sprickerhof-de/pcl
$ sudo apt-get update;
$ sudo apt-get install libpcl-all
    \end{verbatim}

    Others (including Windows): \\
     Run binary executable or compile source from http://pointclouds.org/downloads/


\item Install OctoMap (I used 1.4.2) - http://octomap.sourceforge.net

    Linux Ubuntu:
    \begin{verbatim}
$ sudo apt-get install cmake doxygen libqt4-dev libqt4-opengl-dev
$ cd build && cmake .. && make && sudo make install
    \end{verbatim}

    Windows (Cygwin):
    \begin{verbatim}
$ cd build && cmake .. && make && make install
    \end{verbatim}


\item Install one or more of the following Structure from Motion estimators.
   VisualSFM seems to give the best results, so I recommend going for that one.
   Bundler and Voodoo output files are partly supported, but currently not
   everything will work.

   Website: http://www.cs.washington.edu/homes/ccwu/vsfm/

   \begin{itemize}
   \item VisualSFM (I used 0.5.17)

        Linux (tested on Ubuntu): \\
          Need to install SiftGPU, which needs some hacks in the source code (!)
          Need to install PBA, which needs some hacks in the source code as well
          (include sys/types.h, stdio.h, stdlib.h)
          For GPU acceleration, need to install CUDA as well.
          Otherwise, download Lowe's sift binary (extract binary only to vsfm/bin/):
          http://www.cs.ubc.ca/~lowe/keypoints/ \\

        Windows: \\
          Executable seems to work fine after installing the CUDA toolbox. You may
          get errors concerning some CUDA dll file; search and download it from
          The Internet and put it in the same directory as the VisualSfM executable. \\

        Optionally, one could additionally install CMVS/PMVS for dense reconstruction
        (for comparison only; the dense output is not used for carving).

   \item Voodoo (I used 1.2.0 beta)

        Download binary from:
        http://www.digilab.uni-hannover.de/download.html \\

        Note that Voodoo does not export visibility information for feature points.
        Therefore, important parts of the program (i.e. carving) will not work using
        Voodoo's output. The viewers will work fine.

   \item Bundler (I used 0.4)

        Windows: \\
          Download and install binary from: http://phototour.cs.washington.edu/bundler/

        Linux (Ubuntu/Debian):
        \begin{verbatim}
$ sudo apt-get install gfortran libgfortran3 liblapack-dev libblas-dev \
                     libblacs-mpi-dev libminpack1 libf2c2-dev libann-dev
Compile from source (http://phototour.cs.washington.edu/bundler/)
Need to make some patches as suggested by gcc.
$ sudo cp lib/libANN_char.so /usr/lib/
        \end{verbatim}

   \end{itemize}

\end{enumerate}

